Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-06-08 Submission.Rmd
anxiety LaTeX requirements (excluded correlation table)

author: 
  - name          : "Alicia Stachowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "470M Harvey Hall, 721 3rd Street E, Menomenie, WI, 54751, USA"
    email         : "stachowskia@uwstout.edu"
  - name          : "John Kulas"
    address       : "Minneapolis, MN"
    affiliation   : "2"
  - name          : "Renata Garcia Prieto Palacios Roji"
    address       : "Dallas, TX"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin-Stout"
  - id            : "2"
    institution   : "eRg"
  - id            : "3"
    institution   : "PepsiCo"

@@

csl               : apa7.csl
documentclass     : "interact"
#classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r analysis-preferences}

@@

```{r cortab, results="asis"}

>>>>

author: 
  - Alicia Stachowski, University of Wisconsin, Stout
  - John Kulas, eRg
  - Renata Garcia Prieto Palacios Roji, PepsiCo

@@

csl               : apa7.csl
documentclass     : interact
#classoption       : "man"
output            : pdf_document
---

@@

```{r analysis-preferences, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r cortab, results="asis", eval=FALSE}
